---
title: "DS101"
pagetitle:  "DS101 · TUHH Business Analytics R Programming Guide"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 4
---

[comment]: <> (Set global options for code chunks)
```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(fontawesome)
library(icon)
```

# Getting Started {-}

2020 | 01 | 23 Last compiled: `r Sys.Date()`

Before we meet (online via [zoom](https://zoom.us/download)) for our first class there are few things you should try at home to get started. Each of the assignments are explained in detail in the corresponding course script chapter.  

## Part 1
|#|Assignment|script chapter|
|:-|------------------------|-----:|
|1.1|Download and install R on your computer. This is the R website [https://www.r-project.org](https://www.r-project.org)|<a href="https://tuhh-w11.github.io/data-science/script/docs/installing-r-rstudio-ide.html" target="_blank"><b>1.1</b></a>|
|1.2|Download and install R-studio. You must download and install R first before installing R-studio. The R-studio website is [https://www.rstudio.com](https://www.rstudio.com)|<a href="https://tuhh-w11.github.io/data-science/script/docs/installing-r-rstudio-ide.html" target="_blank"><b>1.1</b></a>|
|1.3|Get familiar with R and RStudio and complete the minor tasks within this chapter|<a href="https://tuhh-w11.github.io/data-science/script/docs/understanding-the-rstudio-ide-working-with-rstudio.html" target="_blank"><b>1.2</b></a>|

## Part 2
|#|Assignment|script chapter|
|:-|------------------------|-----:|
|2.1|Create a free github account. The github website is [https://github.com](https://github.com)|<a href="https://tuhh-w11.github.io/data-science/script/docs/github-github-desktop.html" target="_blank"><b>2.0</b></a>|
|2.2|Download and install github desktop [https://desktop.github.com](https://desktop.github.com)|<a href="https://tuhh-w11.github.io/data-science/script/docs/github-github-desktop.html" target="_blank"><b>2.0</b></a>|
|2.3|Create your own lab journal and host it on github.com [LabJournal](https://tuhh-w11.github.io/lab_journal_website/index.html)|<a href="https://tuhh-w11.github.io/data-science/script/docs/github.html" target="_blank"><b>2.0</b></a>|

Don't worry if you ran into issues with these first steps, we will address them in our first video session. 

## ![](images/datacamp-vector-logo.svg){width=130px}

If you have R-studio working and your github page set up, is there anything else you can do before we meet for the first time? Yes.

You can get started with some of the following tutorials, and you can begin messing around in R. 

Join the NIT data science team on data camp via this link. Please register with your tuhh email address. [datacamp.com](https://www.datacamp.com/groups/shared_links/91287653ed5bd4c0f14e7c60e2d61a62dc1f1ba2afc84a4909665c00cd441f0c)

These tutorials are optional and you can choose whatever <a href="https://learn.datacamp.com/courses/" target="_blank"><b>courses</b></a> you want. In accordance with the content of this session, I would recommend you to complete the following tutorials: 

|#|Course|datacamp-link|script chapter|
|:-|------------------------|-|-:|
|1.|Introduction to R|<a href="https://learn.datacamp.com/courses/free-introduction-to-r" target="_blank"><b>`r icon::fa("globe")` Link</b></a>|2.0|
|2.|Intermediate R|<a href="https://learn.datacamp.com/courses/intermediate-r" target="_blank"><b>`r icon::fa("globe")` Link</b></a>|2.0|


We will be spending the first few weeks of the course working on solving different kinds of business problems in R. These problems will help you learn the ins and outs of coding in R. You can get a head start by trying to solve the problems in this [list of programming challenges](https://crumplab.github.io/programmingforpsych/programming-challenges-i-learning-the-fundamentals.html). 

# Session

2018 | 7 | 23 Last compiled: `r Sys.Date()`

## Part 1
Lorem Ipsum

## Part 2
Lorem Ipsum

## ![](images/datacamp-vector-logo.svg){width=130px}

|#|Course|datacamp-link|script chapter|
|:-|------------------------|-|-:|
|3.|Introduction to the Tidyverse|<a href="https://learn.datacamp.com/courses/introduction-to-the-tidyverse" target="_blank"><b>`r icon::fa("globe")` Link</b></a>|2.0|
|4.|Introduction to Importing Data in R|<a href="https://learn.datacamp.com/courses/introduction-to-importing-data-in-r" target="_blank"><b>`r icon::fa("globe")` Link</b></a>|2.0|

# Session
## Second level

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the sam place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation =1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag), from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You learn all of these things and more can be customized in each R code block.

# Session
## Second level

Use this lab journal to record what you do in R. This way I will be able to see what you are doing and help you along the way. You will also be creating a repository of all the things you do. You can make posts about everything. Learning specific things in R (project unrelated), and doing things for the project that we will discuss at the beginning of the Fall semester. You can get started now by fiddling around with googling things, and trying stuff out in R. I've placed some helpful starting links in the links page on this website