---
title: "Introduction to DS101"
author: ["Joschka Schwarz"]
date: "1/22/2020"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R course material

This class will teach you how to program in R, with hands-on examples. I developed it for non-programmers to provide a friendly introduction to the R language. You'll learn how to load data, assemble and disassemble data objects, navigate R's environment system, write your own functions, and use all of R's programming tools. Throughout the book, you'll use your newfound skills to solve practical data science problems.

If you are already comfortable with R, and would like to focus instead how to analyze data using R's Tidyverse packages, I recommend [R for Data Science](http://r4ds.had.co.nz/), a book that I co-authored with Hadley Wickham. 

This website is (and will always be) __free to use__, and is licensed under the [Creative Commons Attribution-NonCommercial-NoDerivs 4.0](https://creativecommons.org/licenses/by-nc-nd/4.0/) License. If you'd like to give back, please consider reporting a typo or leaving a pull request at [github.com/rstudio-education/hopr](https://github.com/TUHH-W11/r-course-material).


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
